### 2020-06-28 thesis_template/3_Body/chapter/concept.tex
corrected

\section{Introduction}
\label{sec::concept_intro}
This chapter discusses the concepts studied in our experiments. 
Section~\ref{sec:concept_diffval} explains different variable type we can use in Rust programming.
In Section~\ref{sec:concept_refcount}, we explain the advantage and disadvantage of Reference Count in Rust. 
Multithread programming in Rust is studied in Section~\ref{sec:concenpt_multithreading}. 
Two algorithms are discussed used in Big Data processing and examined in our experiments: 
Tree-aggregate in Section~\ref{sec:concept_treeagg} and K-Nearest-Neighbors in Section~\ref{sec:concept_knn}.
Finally, Section~\ref{sec:concept_compobj} shows complex object representations used in our experiments.

\section{Type of Variable}
\label{sec:concept_diffval}
In Rust, there are three variable types: owner, reference, and slice (only for sequence of values). 
A developer is sometimes forced to use specific variable types. For example, some of methods are only implemented to specific variable types.
However, one can select any variable types for operation in most case.

These variables have different memory representation shown in Figure~\ref{fig:own_ref_slice}.
The owner has a pointer pointing to the memory address of sequence values, length of the values, and capacity allocated to store additional values. 
Reference and Slice are variables borrowing value owned by other variable. The reference is a pointer that points to the owner. 
The slice is a pointer that points to memory address of sequence values. It has value such as length of sequence values stored in the memory. 
Since they have different memory representation, an assumption is that it takes different time to access to the contents of the memory among these pointer types.
We examine this by constructing complex objects whose fields are these variable types. The details are explained in Section~\ref{sec:eval_diffval}.

@@

\section{Reference Count}
\label{sec:concept_refcount}
Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
By leveraging Rc, a value can be shared like what borrowing plays the role in Rust programming.

The difference is that Rc checks number of owner pointing to the actual data and makes sure the data is not deleted 
until all the owners are dereferenced. Using Rc is sometimes preferable approach for developers especially when lifetime planning is extremely difficult.
However, the possible problems regarding to Rc are the cost for tracking the number of references and allocating memory on heap instead of stack.
Having these assumption, an experiment is conducted to examine difference of runtime performance of dropping reference and Rc. 
This is explained in section 3.2.

@@

Arc is a simple interface that allows threads to share data. Arc allows multiple variable to have ownerships of a particular value similarly to Rc, 
but also supports atomic feature enabling the ownerships exist in different threads. 
In many situation where developer write a multithreading code, the deletion of Arc happens significant amount of times. 
Similarly to Rc, our assumption is that deletion of Arc has also overhead when we compare to normal reference. 
To assess runtime performances of algorithm with Arc vs normal reference, we implement merge-sort algorithm in two different ways.

\section{Tree-aggregate}
\label{sec:concept_treeagg}
Finally, we implement some of algorithm common in Big Data processing. One of them is tree-aggregate.

Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib \cite{DBLP:journals/jmlr/MengBYSVLFTAOXX16}). 
The topology of aggregation patterns in Apache Spark are shown in Figure~\ref{fig:aggregationk_patttern}. 
In the traditional aggregation function in Spark, results of aggregation in all executor clusters are sent to the driver. 
That is why this operation suffers from the CPU cost in merging partial results and the network bandwidth limit.
Tree-aggregate is a communication pattern which overcomes these problems by breaking aggregate operation in multi-level represented like tree structure.

Spark generates intermediate objects from RDDs. In Tree-aggregation, aggregated HashMap like data structure is created in each thread or node. 
When it aggregates objects in RDD, copy of objects should be performed to construct intermediate aggregated data structure.
In another possible way that might be implemented, one can use reference to the objects to perform aggregation instead of copying the values themselves.
In Rust, we can clone or get Arc (Rc if in single thread) of objects to implement these operations.

Since Tree-aggregation algorithm generates and deletes a lot of intermediate data structures, 
how the data structures are constructed and how they are deallocated is important concern in memory management in this algorithm.
In our experiment, tree-aggregation algorithms are examined in multi-threading. The detail is described in section 3.2.

@@

\section{K-Nearest-Neighbors}
\label{sec:concept_knn}
The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classify targets into categories. 
In training KNN, it simply stores all available training data without calculation. At prediction phase, targets are given and similarity measures are calculated. 
Based on these similarities, the algorithm selects \(K\) (user-defined number) training observations similar to the each target. 
Then, it checks corresponding categories of the \(K\) observations to determine predicted category.

In brute force algorithm, KNN calculates similarity measures for all combinations among training and testing observations. 
If training data has \(N\) observations and test data has \(M\) observations, KNN needs to calculate \(N \times M\) similarity measures. 
Sort or binary heap can be used to select the \(K\) most similar training observations.

In our experiment, KNN algorithms performs document classification and implemented in multithread. 
There are three phases in our algorithm: preprocessing, query, and combine phase. 
In preprocessing phase, the algorithm calculates Term-frequencies (Tfs) to generate numeric feature vectors and matrices. 
In query phase, similarity measures are calculated and \(K\) nearest neighbors are selected. 
For similarity measure, our choice is cosine similarity(~\ref{eq:cosine}). 
In combine phase, results of query phase are gathered and combined from each threads.

@@

Even though preprocessing phase is not specific process for KNN algorithm, 
it is common in algorithms used in Natural Language Processing. Therefore, better memory management strategy should be applied in this preprocessing phase.
This preprocessing generates many intermediate data structures and copies of String elements are used in these data structure again and again. 
We can again either clone or get Arc of String.

Our KNN algorithms are implemented with batch processing. In query phase, we control batch size to examine how size of objects allocated simultaneously in memory has impact to algorithm's runtime performance.
The detail implementation is explained in section3.2.

\section{Complex Objects}
\label{sec:concept_compobj}
To conduct experiments for above concepts, we use the 4 types of complex object: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
These object contains other type of object: OrderOwned, OrderBorrowed, OrderSlice, and OrderRc.
The representation of these objects are shown in Figure~\ref{fig:customer} and Figure~\ref{fig:order}. 
Three Customer objects have 15 fields: 3 fields for i32, 3 fields for f64, 8 fields for String, and 1 field for Order object.
All of fields of CustomerOwned and OrderOwned are owned by the object. On the other hand, fields of CustomerBorrowed, CustomerSlice, OrderBorrowed, and OrderSlice are borrowed. 
Reference of slice of values are used as the fields and owner of actual values are stored differently in source Vec. 
CustomerRc acquires Rc of values used for its fields from the source Vec.

@@

\section{Summary}
\label{sec:concept_summary}
We discussed some of concepts to understand goals of our experiments. 
Theoretical discussions are noted in this chapter, such as assumptions where behavior of different variable types differ from each other, the impact of use of Reference Counting and Atomic Reference Counting, 
and the best practice to implement algorithms used in Big Data processing. In Chapter\ref{chapter:evaluation}, it discusses details setting of our experiments, their results and analysis.

>>>>

\section{Introduction}
\label{sec::concept_intro}
This chapter discusses the concepts studied in our experiments. 
Section~\ref{sec:concept_diffval} explains different variable types we can use in Rust programming.
In Section~\ref{sec:concept_refcount}, we explain the advantages and disadvantages of Reference Count in Rust. 
Multithread programming in Rust is studied in Section~\ref{sec:concenpt_multithreading}. 
Two algorithms are discussed used in Big Data processing and examined in our experiments: 
Tree-aggregate in Section~\ref{sec:concept_treeagg} and K-Nearest-Neighbors in Section~\ref{sec:concept_knn}.
Finally, Section~\ref{sec:concept_compobj} shows complex object representations used in our experiments.

\section{Types of Variables}
\label{sec:concept_diffval}
In Rust, there are three variable types: owner, reference, and slice (only for sequence of values). 
A developer is sometimes forced to use specific variable types. For example, some of methods are only implemented to specific variable types.
However, one can select any variable type for operation in most cases.

These variables have different memory representation shown in Figure~\ref{fig:own_ref_slice}.
The owner has a pointer pointing to the memory address of sequence values, length of the values, and capacity allocated to store additional values. 
Reference and Slice are variables borrowing value owned by other variable. The reference is a pointer that points to the owner. 
The slice is a pointer that points to memory addresses of sequence values. It has values such as length of sequence values stored in the memory. 
Since they have different memory representations, an assumption is that it takes different time to access the contents of the memory among these pointer types.
We examine this by constructing complex objects whose fields are these variable types. The details are explained in Section~\ref{sec:eval_diffval}.

@@

\section{Reference Count}
\label{sec:concept_refcount}
References are useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
By leveraging Rc, a value can be shared like what borrowing plays the role in Rust programming.

The difference is that Rc checks the number of owners pointing to the actual data and makes sure the data is not deleted 
until all the owners are dereferenced. Using Rc is sometimes the preferred approach for developers especially when lifetime planning is extremely difficult.
However, the possible problems regarding Rc are the cost for tracking the number of references and allocating memory on heaps instead of stacks.
Having these assumption, an experiment is conducted to examine difference of runtime performance of dropping reference and Rc. 
This is explained in section 3.2.

@@

Arc is a simple interface that allows threads to share data. Arc allows multiple variable to have ownerships of a particular value similarly to Rc, 
but also supports atomic feature enabling the ownerships exist in different threads. 
In many situation where developers write a multithreading code, the deletion of Arc happens a significant amount of times. 
Similarly to Rc, our assumption is that deletion of Arc also has overhead when we compare to normal references. 
To assess runtime performances of algorithm with Arc vs normal references, we implement merge-sort algorithm in two different ways.

\section{Tree-aggregate}
\label{sec:concept_treeagg}
Finally, we implement some of common algorithms in Big Data processing. One of them is tree-aggregate.

Tree-aggregate is a communication patten heavily used for Machine Learning algorithms in Spark (MLlib \cite{DBLP:journals/jmlr/MengBYSVLFTAOXX16}). 
The topology of aggregation patterns in Apache Spark are shown in Figure~\ref{fig:aggregationk_patttern}. 
In the traditional aggregation functions in Spark, results of aggregation in all executor clusters are sent to the driver. 
That is why this operation suffers from the CPU cost in merging partial results and the network bandwidth limit.
Tree-aggregate is a communication pattern which overcomes these problems by breaking aggregate operation in multi-level represented like tree structure.

Spark generates intermediate objects from RDDs. In Tree-aggregation, aggregated HashMap like data structure is created in each thread or node. 
When it aggregates objects in RDD, copies of objects should be performed to construct intermediate aggregated data structure.
In another possible way that might be implemented, one can use references to the objects to perform aggregation instead of copying the values themselves.
In Rust, we can clone or get Arc (Rc if in single thread) of objects to implement these operations.

Since Tree-aggregation algorithms generate and delete a lot of intermediate data structures, 
how the data structures are constructed and how they are deallocated is an important concern in memory management in this algorithm.
In our experiment, tree-aggregation algorithms are examined in multi-threading. The detail is described in section 3.2.

@@

\section{K-Nearest-Neighbors}
\label{sec:concept_knn}
The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classifies targets into categories. 
In training KNN, it simply stores all available training data without calculation. At prediction phase, targets are given and similarity measures are calculated. 
Based on these similarities, the algorithm selects \(K\) (user-defined number) training observations similar to each target. 
Then, it checks corresponding categories of the \(K\) observations to determine predicted categories.

In brute force algorithm, KNN calculates similarity measures for all combinations among training and testing observations. 
If training data has \(N\) observations and test data has \(M\) observations, KNN needs to calculate \(N \times M\) similarity measures. 
Sort or binary heaps can be used to select the \(K\) most similar training observations.

In our experiment, KNN algorithms performs document classification and implemented in multithread. 
There are three phases in our algorithm: preprocessing, query, and combine phase. 
The preprocessing phase, the algorithm calculates Term-frequencies (Tfs) to generate numeric feature vectors and matrices. 
In the query phase, similarity measures are calculated and \(K\) nearest neighbors are selected. 
For similarity measure, our choice is cosine similarity(~\ref{eq:cosine}). 
In the combine phase, results of query phase are gathered and combined from each threads.

@@

Even though the preprocessing phase is not specific process for KNN algorithm, 
it is common in algorithms used in Natural Language Processing. Therefore, better memory management strategy should be applied in this preprocessing phase.
This preprocessing generates many intermediate data structures and copies of String elements are used in these data structure again and again. 
We can again either clone or get Arc of String.

Our KNN algorithms are implemented with batch processing. In query phase, we control batch size to examine how size of objects allocated simultaneously in memory has impact to algorithm's runtime performance.
The detailed implementation is explained in section 3.2.

\section{Complex Objects}
\label{sec:concept_compobj}
To conduct experiments for the above concepts, we use 4 types of complex objects: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
These objects contain other type of objects: OrderOwned, OrderBorrowed, OrderSlice, and OrderRc.
The representation of these objects are shown in Figure~\ref{fig:customer} and Figure~\ref{fig:order}. 
Three Customer objects have 15 fields: 3 fields for i32, 3 fields for f64, 8 fields for String, and 1 field for Order object.
All fields of CustomerOwned and OrderOwned are owned by the object. On the other hand, fields of CustomerBorrowed, CustomerSlice, OrderBorrowed, and OrderSlice are borrowed. 
References of slices of values are used as the fields and owners of actual values are stored differently in source Vec. 
CustomerRc acquires Rc of values used for its fields from the source Vec.

@@

\section{Summary}
\label{sec:concept_summary}
We discussed some concepts to understand goals of our experiments. 
Theoretical discussions are noted in this chapter, such as assumptions where behavior of different variable types differ from each other, the impact of use of Reference Counting and Atomic Reference Counting, 
and the best practice to implement algorithms used in Big Data processing. In Chapter\ref{chapter:evaluation}, we discuss detailed settings of our experiments, their results and analysis.

### 2020-06-28 thesis_template/3_Body/chapter/evaluation.tex
corrected

\section{Introduction}
\label{sec:eval_intro}
In this chapter, detail experiment settings, executions and results are discussed.
Section~\ref{sec:eval_setdetail} details hardware configurations and data set we use. 
There are 5 experiments conducted. In Section~\ref{sec:eval_diffval}, we discuss the experiment 
where we assess runtime to access object's field with different variable types. 
Section~\ref{sec:eval_refcount} shows details to examine how behaviors of normal reference and Reference Count are different. 
Section~\ref{sec:eval_sort} describes our Merge-sort experiment to examine behavior of Atomic Reference Counting.
Two algorithms are discussed used in Big Data processing and examined in our experiments: 
Tree-aggregate in Section~\ref{sec:concept_treeagg} and K-Nearest-Neighbors in Section~\ref{sec:concept_knn}.

@@

\section{Experiment 1: Accessing Object with Different Variable Type}
\label{sec:eval_diffval}
\input{3_Body/model/access_own_reference_slice}

@@

\section{Summary}
\label{sec:eval_summary}
In this chapter, we examines various memory management strategies for different algorithms in Rust programming.
There are many factors that might differ performance of algorithms: different variable type, Reference Counting, Atomic Reference Counting, and frequency of memory de/allocation.
We should select the best memory management strategies when developing Big Data processing tools. 
Some of tips for the development are proved in our experiments. We conclude this thesis in Chapter~\ref{chapter:Conclusions}.

>>>>

\section{Introduction}
\label{sec:eval_intro}
In this chapter, detailed experiment settings, executions and results are discussed.
Section~\ref{sec:eval_setdetail} details hardware configurations and datasets we use. 
There are 5 experiments conducted. In Section~\ref{sec:eval_diffval}, we discuss the experiment 
where we assess runtime to access object's fields with different variable types. 
Section~\ref{sec:eval_refcount} shows details to examine how behaviors of normal reference and Reference Count are different. 
Section~\ref{sec:eval_sort} describes our Merge-sort experiment to examine behavior of Atomic Reference Counting.
Two algorithms are used in Big Data processing and examined in our experiments: 
Tree-aggregate in Section~\ref{sec:concept_treeagg} and K-Nearest-Neighbors in Section~\ref{sec:concept_knn}.

@@

\section{Experiment 1: Accessing Objects with Different Variable Types}
\label{sec:eval_diffval}
\input{3_Body/model/access_own_reference_slice}

@@

\section{Summary}
\label{sec:eval_summary}
In this chapter, we examine various memory management strategies for different algorithms in Rust programming.
There are many factors that might differ performance of algorithms: different variable type, Reference Counting, Atomic Reference Counting, and frequency of memory de/allocation.
We should select the best memory management strategies when developing Big Data processing tools. 
Some tips for the development are proven in our experiments. We conclude this thesis in Chapter~\ref{chapter:Conclusions}.

### 2020-06-28 thesis_template/3_Body/model/access_own_reference_slice.tex
corrected

This experiment is conducted to provide answers to the following two questions. One is how different variable types have impact to runtime performance.
The other is how initialization of Vec size has impact to runtime performance. 
In this experiment, we focus on owner, reference, and slice as a variable of sequence values. 
Since these variables have different memory representation, there might be differences among time for access to actual values of each variables.

To evaluate this assumption, we use the three types of complex object: CustomerOwned, CustomerBorrowed and CustomerSlice. 
At first, we generate source Vecs for all fields, Vecs which contain all elements used for corresponding fields of objects.
For example, all of i32 elements used for key field in 1 million Customer object are stored in Vec$<$i32$>$ with 1 million i32 elements. 
Later, these i32 elements are moved to be owned or borrowed by the object's fields.

Next, 3, 13, 23, 33 million of Customer objects are created and stored in Vec. 
When a Customer Vec is created, whether size of Vec is initialized is controlled. 
Finally, serialization of Customer object is performed as an operation forcing program to access all of fields in the object.
This serialization is performed each Customer objects in the Vec. We measure total runtime to serialize all of Customer objects 
stored in Vec.

\subsection{Result}
\label{sec:history}
The result is shown in Figure~\ref{fig:rustaccessinit} and Figure~\ref{fig:rustaccessnoinit}.
Figure~\ref{fig:rustaccessinit} is comparison of the runtime performance among different Customer object types with Vec size initialization.
Figure~\ref{fig:rustaccessnoinit} is comparison in the same set of experiment except Vec size is not initialized. 
The blue, yellow, and green chats represent runtime of access to fields of CustomerOwned, CustomerBorrowed, and CustomerSlice objects respectively.

No matter Vec size initialized or not, differences of runtime for accessing objects are not remarkable among different object types.

@@

\subsection{Discussion}
\label{sec:history}
Difference of variable types does not have huge impact to runtime of accessing to actual value.
Even thought owner, reference , and slice have different memory representations, the access time to its value is 
close to each other. As shown in Figure~\ref{fig:own_ref_slice}, the representations of owner and slice are almost identical except slice does not have capacity for values.
Reference is pointer pointing to owner, so it has an additional step to access actual value. 
However, the result shows this additional step does not have huge impact for runtime to access memory region of the value.

>>>>

This experiment is conducted to provide answers to the following two questions. One is how different variable types impact runtime performance.
The other is how initialization of Vec size impacts runtime performance. 
In this experiment, we focus on owner, reference, and slice as variables of sequence values. 
Since these variables have different memory representation, there might be differences among time for access to actual values of each variables.

To evaluate this assumption, we use the three types of complex objects: CustomerOwned, CustomerBorrowed and CustomerSlice. 
At first, we generate source Vecs for all fields, Vecs which contain all elements used for corresponding fields of objects.
For example, all of i32 elements used for key field in 1 million Customer object are stored in Vec$<$i32$>$ with 1 million i32 elements. 
Later, these i32 elements are moved to be owned or borrowed by the objects' fields.

Next, 3, 13, 23, 33 million Customer objects are created and stored in Vec. 
When a Customer Vec is created, whether size of Vec is initialized is controlled. 
Finally, serialization of Customer object is performed as an operation forcing the program to access all of fields in the object.
This serialization is performed for each Customer objects in the Vec. We measure total runtime to serialize all of Customer objects 
stored in Vec.

\subsection{Result}
\label{sec:history}
The result is shown in Figure~\ref{fig:rustaccessinit} and Figure~\ref{fig:rustaccessnoinit}.
Figure~\ref{fig:rustaccessinit} is a comparison of the runtime performance among different Customer object types with Vec size initialization.
Figure~\ref{fig:rustaccessnoinit} is a comparison in the same set of experiment except Vec size is not initialized. 
The blue, yellow, and green bars represent runtime of access to fields of CustomerOwned, CustomerBorrowed, and CustomerSlice objects respectively.

Whether Vec size is initialized or not, differences of runtime for accessing objects are not remarkable among different object types. 
The memory usage for algorithms with 33 million of Customer objects are about 26G bytes for any type of variable.

@@

\subsection{Discussion}
\label{sec:history}
Difference of variable types does not have huge impact to runtime of accessing to actual value.
Even though owner, reference , and slice have different memory representations, the access time to its value is 
close to each other. As shown in Figure~\ref{fig:own_ref_slice}, the representations of owner and slice are almost identical except slice does not have capacity for values.
Reference is pointer pointing to owner, so it has an additional step to access actual value. 
However, the result shows this additional step does not have huge impact for runtime to access memory region of the value.

### 2020-06-28 thesis_template/3_Body/model/drop_ref_rc.tex
corrected

In this experiment, CustomerBorrowed and CustomerRc are used to see difference of dropping time among reference and Rc. 
In the CustomerRc and OrderRc struct, all fields take Rc (Rc$<$T$>$). Similarly to the experiment in the last section, 
sets of integer, float, and String vector are created and their elements are borrowed or reference counted to create CustomerBorrowed or CustomerRc objects.
The dropping of objects deletes references or Rcs used for fields of the objects. However, it does not deallocate values to which they are pointing. 
Therefore, the evaluated runtime of dropping objects only consists of dropping time of reference or Rc, but deallocation time.
We generated 10, 20, 30, and 40 million of CustomerBorrowed and CustomerRc objects and performed drop one by one.

@@

\subsection{Discussion}
In this experiment, an assessment is conducted to verify whether there is difference between behavior of reference and Rc.
The reason why dropping Rc is much slower than dropping reference is that Rc requires runtime overhead to check some states of the variable, 
but when to drop reference is already determined at compile time. When dropping Rc, Rc has to check the number of variable pointing to the actual content and decide 
deallocate the memory or not. However, memory management and lifetime strategy of reference is already determined at compile time.
This determination of memory management strategy at compile increases runtime performance of dropping complex object constructed with reference type variable.
This may say that we should use reference whenever high performance computation is critical.

However, dealing with reference is sometimes cumbersome. Tracking lifetime of reference can be done easily in simple situation. 
But, if we have complex objects constructed with fields of reference, the lifetime tracking become extremely difficult. 
For example, constructing nested objects with reference fields require a developer to plan memory management with many lifetime symbols. 
Using reference counting eliminates developer's responsibility to specify lifetime of variables. 
This may ease and speed up development process, and increase understandability of codes.

Even though we have stack allocated values, such as i32 and f64, in Rc in our experiment, 
one should avoid wrapping stack allocated values in Rc. Wrapping value in Rc allocates heap memory so that allocating Rc$<$i32$>$ or Rc$<$f64$>$ unnecessarily use space of 
heap. Additionally, stack allocated values are usually easy to be copied. Therefore, developer does not have to even use reference; one can just copy the value. 
Copying value in Rust is to copy the original value and to assign the copy to new owner variable.

>>>>

In this experiment, CustomerBorrowed and CustomerRc are used to see difference of dropping time among reference and Rc. 
In the CustomerRc and OrderRc struct, all fields take Rc (Rc$<$T$>$). Similarly to the experiment in the last section, 
sets of integer, float, and String vector are created and their elements are borrowed or reference counted to create CustomerBorrowed or CustomerRc objects.
The dropping of objects deletes references or Rcs used for fields of the objects. However, it does not deallocate values to which they are pointing. 
Therefore, the evaluated runtime of dropping objects only consists of dropping time of reference or Rc, but deallocation time.
We generated 10, 20, 30, and 40 million CustomerBorrowed and CustomerRc objects and performed drop one by one.

@@

\subsection{Discussion}
In this experiment, an assessment is conducted to verify whether there is difference between behavior of reference and Rc.
The reason why dropping Rc is much slower than dropping reference is that Rc requires runtime overhead to check some states of the variable, 
but when to drop reference is already determined at compile time. When dropping Rc, Rc has to check the number of variables pointing to the actual content and decide 
whether to deallocate the memory or not. However, memory management and lifetime strategy of reference is already determined at compile time.
This determination of memory management strategy at compile increases runtime performance of dropping complex object constructed with reference type variable.
This may say that we should use reference whenever high performance computation is critical.

However, dealing with reference is sometimes cumbersome. Tracking lifetime of reference can be done easily in simple situation. 
But, if we have complex objects constructed with fields of reference, the lifetime tracking becomes extremely difficult. 
For example, constructing nested objects with reference fields requires a developer to plan memory management with many lifetime symbols. 
Using reference counting eliminates the developer's responsibility to specify lifetime of variables. 
This may ease and speed up development process, and increase understandability of codes.

Even though we have stack allocated values, such as i32 and f64, in Rc in our experiment, 
one should avoid wrapping stack allocated values in Rc. Wrapping value in Rc allocates heap memory so that allocating Rc$<$i32$>$ or Rc$<$f64$>$ unnecessarily uses space of 
heap. Additionally, stack allocated values are usually easy to be copied. Therefore, developer does not have to even use reference; one can just copy the value. 
Copying value in Rust is to copy the original value and to assign the copy to new owner variable.

### 2020-06-28 thesis_template/3_Body/model/experimental_set_detail.tex
corrected

We have used two different data sets. One is a real-world data set, Wikipedia page data set,
and another is a syntactic randomized generated data set based on Complex object described in Section~\ref{sec:concept_compobj}. 
We use one machine with particular specification.
\subsection{Wikipedia Data Sets}
 \label{sec:concept_dataset}
 Wikipedia page data sets are used to perform document classification with KNN. 
 We have separated the data set into training and test data set, 
 \(10^5\) pages are used for training data set, and 18724 pages are used for target.

>>>>

We have used two different datasets. One is a real-world data set, Wikipedia page data set,
and another is a syntactic randomized generated data set based on Complex objects described in Section~\ref{sec:concept_compobj}. 
We use one machine with particular specifications.
\subsection{Wikipedia Data Sets}
 \label{sec:concept_dataset}
 Wikipedia page data sets are used to perform document classification with KNN. 
 We have separated the data set into training and test data set, 
 \(10^5\) pages are used for training data set, and 18724 pages are used for target.
